### 2025-04-15 reports/paper/resources/intervention-density-witnin-combos-a.tex
cannot figure out figure

% Created by tikzDevice version 0.12.3.1 on 2023-08-04 14:49:59
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (252.94,180.68);
\end{scope}
\begin{scope}
\path[clip] ( 38.22, 31.50) rectangle (246.94,165.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 38.22, 31.50) rectangle (246.94,165.68);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01,110.79);

\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31, 37.60);

@@

\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.90, 62.00);

\path[fill=fillColor] ( 76.90, 37.60) rectangle ( 84.20, 37.60);

@@

\path[fill=fillColor] ( 91.50, 37.60) rectangle ( 98.80, 37.60);

\path[fill=fillColor] ( 98.80, 37.60) rectangle (106.10, 37.60);

\path[fill=fillColor] (106.10, 37.60) rectangle (113.39, 37.60);

\path[fill=fillColor] (113.39, 37.60) rectangle (120.69,159.58);

@@

\path[fill=fillColor] (135.29, 37.60) rectangle (142.58, 37.60);

\path[fill=fillColor] (142.58, 37.60) rectangle (149.88, 37.60);

@@

\path[fill=fillColor] (171.78, 37.60) rectangle (179.07, 37.60);

\path[fill=fillColor] (179.07, 37.60) rectangle (186.37, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01,110.79);

\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.90, 62.00);

\path[draw=drawColor,line width= 0.4pt] ( 76.90, 37.60) rectangle ( 84.20, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] ( 91.50, 37.60) rectangle ( 98.80, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 98.80, 37.60) rectangle (106.10, 37.60);

\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.39, 37.60);

\path[draw=drawColor,line width= 0.4pt] (113.39, 37.60) rectangle (120.69, 62.00);

@@

\path[draw=drawColor,line width= 0.4pt] (127.99, 37.60) rectangle (135.29, 62.00);

\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.58, 37.60);

\path[draw=drawColor,line width= 0.4pt] (142.58, 37.60) rectangle (149.88, 62.00);

\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] (164.48, 37.60) rectangle (171.78, 37.60);

\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.07, 37.60);

\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 37.60);

\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 62.00);

@@

\path[draw=drawColor,line width= 0.4pt] (200.97, 37.60) rectangle (208.27, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16, 62.00);

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (120.69, 31.50) -- (120.69,165.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.22, 31.50) rectangle (246.94,165.68);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 34.85) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 62.29) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 89.74) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,117.18) {15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,144.62) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 37.60) --
	( 38.22, 37.60);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 65.05) --
	( 38.22, 65.05);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 92.49) --
	( 38.22, 92.49);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,119.93) --
	( 38.22,119.93);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,147.38) --
	( 38.22,147.38);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 47.71, 28.75) --
	( 47.71, 31.50);

\path[draw=drawColor,line width= 0.4pt,line join=round] (106.10, 28.75) --
	(106.10, 31.50);

\path[draw=drawColor,line width= 0.4pt,line join=round] (164.48, 28.75) --
	(164.48, 31.50);

\path[draw=drawColor,line width= 0.4pt,line join=round] (222.86, 28.75) --
	(222.86, 31.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (142.58,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[fill=fillColor] (168.95,143.84) rectangle (244.95,163.87);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,157.35) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,146.34) rectangle (176.95,154.34);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (172.95,146.34) -- (172.95,154.34);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,147.59) {0.25 mg/m$^3$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,113.81) rectangle (240.85,141.84);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,135.32) {Distribution:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,124.31) rectangle (176.95,132.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] (168.95,124.31) rectangle (176.95,132.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,116.31) rectangle (176.95,124.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] (169.45,116.81) rectangle (176.45,123.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,125.55) {Post-intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,117.55) {Observed};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  2.22,170.34) {a)};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2025-04-15 00:28:30
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (252.94,180.68);
\end{scope}
\begin{scope}
\path[clip] ( 38.23, 31.51) rectangle (246.94,165.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 38.23, 31.51) rectangle (246.94,165.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01, 37.60);

\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31, 46.99);

@@

\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.91, 46.99);

\path[fill=fillColor] ( 76.91, 37.60) rectangle ( 84.20, 46.99);

@@

\path[fill=fillColor] ( 91.50, 37.60) rectangle ( 98.80, 46.99);

\path[fill=fillColor] ( 98.80, 37.60) rectangle (106.10,159.58);

\path[fill=fillColor] (106.10, 37.60) rectangle (113.40, 37.60);

\path[fill=fillColor] (113.40, 37.60) rectangle (120.69, 37.60);

@@

\path[fill=fillColor] (135.29, 37.60) rectangle (142.59, 37.60);

\path[fill=fillColor] (142.59, 37.60) rectangle (149.88, 37.60);

@@

\path[fill=fillColor] (171.78, 37.60) rectangle (179.08, 37.60);

\path[fill=fillColor] (179.08, 37.60) rectangle (186.37, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 46.99);

@@

\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.91, 46.99);

\path[draw=drawColor,line width= 0.4pt] ( 76.91, 37.60) rectangle ( 84.20, 46.99);

@@

\path[draw=drawColor,line width= 0.4pt] ( 91.50, 37.60) rectangle ( 98.80, 46.99);

\path[draw=drawColor,line width= 0.4pt] ( 98.80, 37.60) rectangle (106.10, 46.99);

\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.40, 37.60);

\path[draw=drawColor,line width= 0.4pt] (113.40, 37.60) rectangle (120.69, 37.60);

@@

\path[draw=drawColor,line width= 0.4pt] (127.99, 37.60) rectangle (135.29, 46.99);

\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.59, 37.60);

\path[draw=drawColor,line width= 0.4pt] (142.59, 37.60) rectangle (149.88, 37.60);

\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 93.90);

@@

\path[draw=drawColor,line width= 0.4pt] (164.48, 37.60) rectangle (171.78, 46.99);

\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.08, 37.60);

\path[draw=drawColor,line width= 0.4pt] (179.08, 37.60) rectangle (186.37, 37.60);

\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 46.99);

@@

\path[draw=drawColor,line width= 0.4pt] (200.97, 37.60) rectangle (208.27, 56.37);

@@

\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16, 46.99);

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (120.69, 31.51) -- (120.69,165.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.23, 31.51) rectangle (246.94,165.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 34.85) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28, 74.72) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28,114.60) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.28,154.48) {30};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 37.60) --
	( 38.23, 37.60);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48, 77.48) --
	( 38.23, 77.48);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48,117.36) --
	( 38.23,117.36);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.48,157.23) --
	( 38.23,157.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 47.71, 28.76) --
	( 47.71, 31.51);

\path[draw=drawColor,line width= 0.4pt,line join=round] (106.10, 28.76) --
	(106.10, 31.51);

\path[draw=drawColor,line width= 0.4pt,line join=round] (164.48, 28.76) --
	(164.48, 31.51);

\path[draw=drawColor,line width= 0.4pt,line join=round] (222.86, 28.76) --
	(222.86, 31.51);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (142.59,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[fill=fillColor] (168.95,144.09) rectangle (244.95,164.62);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,158.10) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,146.59) rectangle (176.95,154.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (172.95,146.59) -- (172.95,154.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,147.84) {0.25 mg/m$^3$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,113.06) rectangle (240.85,141.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,135.07) {Distribution:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,123.56) rectangle (176.95,131.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] (168.95,123.56) rectangle (176.95,131.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,115.56) rectangle (176.95,123.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] (169.45,116.06) rectangle (176.45,123.06);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,124.80) {Post-intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,116.80) {Observed};
\end{scope}
\end{tikzpicture}
